On existence of integral point sets and their diameter bounds \footnote{ This work was carried out at Voronezh State University and supported by the Russian Science Foundation grant 19-11-00197. }

### 2020-03-25 pps-linear-bound/pps-linear-lower-bound.tex
[J220][auto] Only referenced equations are numbered
Switch to homemade AJC style
[J220] Switch to bibitems

\usepackage[backend=biber,bibstyle=ieee,citestyle=numeric,sorting=nyt]{biblatex}
\DeclareFieldFormat{sentencecase}{#1}
\addbibresource{../common/notmy.bib}
\addbibresource{../common/my.bib}

%\usepackage{cite}

\usepackage{biblatex2bibitem}

@@

@@

\printbibliography

\printbibitembibliography

>>>>

%\usepackage[backend=biber,style=ajc2020unofficial]{biblatex}
%\addbibresource{../common/notmy.bib}
%\addbibresource{../common/my.bib}

\usepackage{cite}

%\usepackage{biblatex2bibitem}

@@

%Only referenced equations are numbered
\let\etoolboxforlistloop\forlistloop % save the good meaning of \forlistloop
\usepackage{mathtools}
\mathtoolsset{showonlyrefs}
\let\forlistloop\etoolboxforlistloop % restore the good meaning of \forlistloop

% https://tex.stackexchange.com/questions/220268/biblatex-and-autonum-dont-work-together

%\mathtoolsset{showonlyrefs=false}
% (write an equation/multline to be force-numbered here)
%\mathtoolsset{showonlyrefs=true}

@@

%\printbibliography

%\printbibitembibliography

\begin{thebibliography}{99}
%
\bibitem{anning1945integral}
N. H. Anning and P. Erdős, Integral distances, \emph{Bull. Amer. Math. Soc.} 51.\textbf{8} (1945), 598–600, \textsc{doi}: \href
{https://doi.org/10.1090/S0002-9904-1945-08407-9} {\nolinkurl {10.1090/S0002-9904-1945-08407-9}}.
%
\bibitem{antonov2008maximal}
A. R. Antonov and S. Kurz, Maximal integral point sets over {$\mathbb {Z}^2$}, \emph{Int. J. Comput. Math.} 87.\textbf{12}
(2008), 2653–2676, \textsc{doi}: \href {https://doi.org/10.1080/00207160902993636} {\nolinkurl {10.1080/00207160902993636}},
arXiv: \href {http://arxiv.org/abs/0804.1280} {\nolinkurl {0804.1280}}.
%
\bibitem{our-mz-rus-translit}
N. N. Avdeev and E. M. Semenov, On point sets in the plane with integral distances (О множествах точек на плоскости с
целочисленными расстояниями), \emph{Matematicheskie zametki} 100.\textbf{5} (2016), 757–761.
%
\bibitem{our-vmmsh-2018-translit}
N. N. Avdeev and E. M. Semenov, Integral point sets in the plane and Euclidean space (Множества точек с целочисленными
расстояниями на плоскости и в евклидовом пространстве), \emph{Matematicheskij forum (Itogi nauki. Yug Rossii)} (2018),
217–236.
%
\bibitem{avdeev2019particular}
N. N. Avdeev, R. E. Zvolinsky, and E. A. Momot, On particular diameter bounds for integral point sets in higher dimensions
(2019), arXiv: \href {http://arxiv.org/abs/1909.10386} {\nolinkurl {1909.10386}}, \textsc{url}: \url
{https://ui.adsabs.harvard.edu/abs/2019arXiv190910386A/abstract}.
%
\bibitem{bat2018number}
G. Bat-Ochir, On the number of points with pairwise integral distances on a circle, \emph{Discrete Appl. Math.} 254 (2018),
17–32, \textsc{doi}: \href {https://doi.org/10.1016/j.dam.2018.07.004} {\nolinkurl {10.1016/j.dam.2018.07.004}}.
%
\bibitem{costa2013valid}
A. Costa, Valid constraints for the point packing in a square problem, \emph{Discrete Appl. Math.} 161.\textbf{18} (2013),
2901–2909.
%
\bibitem{erdos1945integral}
P. Erdős, Integral distances, \emph{Bull. Amer. Math. Soc.} 51.\textbf{12} (1945), 996, \textsc{doi}: \href
{https://doi.org/10.1090/S0002-9904-1945-08490-0} {\nolinkurl {10.1090/S0002-9904-1945-08490-0}}.
%
\bibitem{garibaldi2005erdos}
J. Garibaldi and A. Iosevich, The Erdős distance problem: lecture notes (2005).%
\bibitem{harborth1993upper}
H. Harborth, A. Kemnitz, and M. Möller, An upper bound for the minimum diameter of integral point sets, \emph{Discrete
Comput. Geom.} 9.\textbf{4} (1993), 427–432, \textsc{doi}: \href {https://doi.org/10.1007/bf02189331} {\nolinkurl
{10.1007/bf02189331}}.
%
\bibitem{kurz2005characteristic}
S. Kurz, On the characteristic of integral point sets in {$\mathbb {E}^m$}, \emph{Australas. J. Combin.} 36 (2006), 241–248,
arXiv: \href {http://arxiv.org/abs/math/0511704} {\nolinkurl {math/0511704}}.
%
\bibitem{kurz2008bounds}
S. Kurz and R. Laue, Bounds for the minimum diameter of integral point sets, \emph{Australas. J. Combin.} 39 (2007), 233–240,
arXiv: \href {http://arxiv.org/abs/0804.1296} {\nolinkurl {0804.1296}}.
%
\bibitem{kurz2008minimum}
S. Kurz and A. Wassermann, On the minimum diameter of plane integral point sets, \emph{Ars Combin.} 101 (2011), 265–287,
arXiv: \href {http://arxiv.org/abs/0804.1307} {\nolinkurl {0804.1307}}.
%
\bibitem{locatelli2002packing}
M. Locatelli and U. Raber, Packing equal circles in a square: a deterministic global optimization approach, \emph{Discrete Appl.
Math.} 122.\textbf{1-3} (2002), 139–166.
%
\bibitem{noll1989nclusters}
L. C. Noll and D. I. Bell, {$n$}-clusters for {$1<n<7$}, \emph{Math. Comp.} 53.\textbf{187} (1989), 439–444.
%
\bibitem{nozaki2013lower}
H. Nozaki, Lower bounds for the minimum diameter of integral point sets, \emph{Australas. J. Combin.} 56 (2013), 139–143.
%
\bibitem{piepmeyer1996maximum}
L. Piepmeyer, The maximum number of odd integral distances between points in the plane, \emph{Discrete Comput. Geom.}
16.\textbf{1} (1996), 113–115, \textsc{doi}: \href {https://doi.org/10.1007/bf02711135} {\nolinkurl {10.1007/bf02711135}}.
%
\bibitem{solymosi2003note}
J. Solymosi, Note on integral distances, \emph{Discrete Comput. Geom.} 30.\textbf{2} (2003), 337–342, \textsc{doi}: \href
{https://doi.org/10.1007/s00454-003-0014-7} {\nolinkurl {10.1007/s00454-003-0014-7}}.
%
\bibitem{solymosi2010question}
J. Solymosi and F. De Zeeuw, On a question of Erdős and Ulam, \emph{Discrete Comput. Geom.} 43.\textbf{2} (2010), 393–401,
arXiv: \href {http://arxiv.org/abs/0806.3095} {\nolinkurl {0806.3095}}.
\end{thebibliography}
